---
title: "Example Presentation"
subtitle: <h2>Subtitle</h2>
          <h1>Author</h1>
author: <br><br>
        Seminar <br>
        LMES
output: 
  revealjs::revealjs_presentation:
    self_contained: false
    keep_md: true
    reveal_plugins: ["notes", "chalkboard", "menu"]
    reveal_options:
      chalkboard: 
        theme: zenburn
        toggleNotesButton: true
      menu:
        numbers: true
---

```{r setup, include=FALSE}
library(rgl)
library(predict3d)
library(MASS)
knitr::opts_chunk$set(echo = FALSE)
knitr::knit_hooks$set(webgl = hook_webgl)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

<aside class="notes">
Here are some notes.
</aside>

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## MathJax

$$(X'X)^{-1} X'y$$
